\textbf{\supplement}\vskip 2ex \mytitle\vskip 2ex

### 2023-02-27 generated/make-help.tex
Mainly getting mathematica+make to work together

% 1 - make all
% 2 - make archive
% 3 - make check-same
% 4 - make check-update
% 5 - make check-versions
% 6 - make data
% 7 - make expand
% 8 - make help
% 9 - make help-brief
% 10 - make mathematica
% 11 - make one-file
% 12 - make pdf
% 13 - make push
% 14 - make readme
% 15 - make really-tidyup
% 16 - make tidyup
% 17 - make zip
% 18 - make zip-data
{\sf\begin{tabular}{rp{4.5in}}
\texttt{make all}&   Analyze the data, then typeset the main PDF files (\texttt{paper-seb-main.pdf} and \texttt{paper-seb-supplementary-material.pdf}).\\
\multicolumn{1}{l@{\vdots}}{}&\\
\texttt{make data}&   Analyze the data, and generate all the data files, the Unix scripts, the CSV, and \LaTeX\ files (including the \LaTeX\ summary of this makefile), etc. In particular, this runs \texttt{node programs/data.js}, downloads the Git repositories used in the pilot survey, and then analyzes them. Note that downloading all the repositories in a reasonable time needs decent internet bandwidth.\\
\multicolumn{1}{l@{\vdots}}{}&\\
\texttt{make help}&   Explain how to use \texttt{make}, and list all available options for using \texttt{make}.\\
\multicolumn{1}{l@{\vdots}}{}&\\
\texttt{make one-file}&   Make a single PDF file paper-seb.pdf (i.e., paper + appendix) all in one.\\
\multicolumn{1}{l@{\vdots}}{}&\\
\texttt{make tidyup}&   Tidyup before doing a git commit. Remove all easily generated files, and the large Git repositories needed for the pilot survey. Do not remove the main PDFs, or the \LaTeX\ data include files.\\
\end{tabular}}

>>>>

% Edit makefile to change the selected make command choices, as follows:
% 1 - make all
% 2 - make archive
% 3 - make check-same
% 4 - make check-update
% 5 - make check-versions
% 6 - make data
% 7 - make expand
% 8 - make help
% 9 - make help-brief
% 10 - make mathematica
% 11 - make mathematica-open
% 12 - make one-file
% 13 - make pdf
% 14 - make push
% 15 - make readme
% 16 - make really-tidyup
% 17 - make tidyup
% 18 - make zip
% 19 - make zip-data

{\sf\begin{tabular}{rp{4.5in}}

\texttt{make all}&
      Analyze the data, then typeset the main PDF files (\texttt{paper-seb-main.pdf} and \texttt{paper-seb-supplementary-material.pdf}).\\
   \multicolumn{1}{l@{\vdots}}{}&\\

\texttt{make data}&
      Analyze the data, and generate all the data files, the Unix scripts, the CSV, and \LaTeX\ files (including the \LaTeX\ summary of this makefile), etc. This \texttt{make} option runs \texttt{node programs/data.js}, downloads the Git repositories used in the pilot survey, and then analyzes them. Note that downloading all the repositories in a reasonable time needs decent internet bandwidth.\\
   \multicolumn{1}{l@{\vdots}}{}&\\

\texttt{make help}&
      Explain how to use \texttt{make}, and list all available options for using \texttt{make}.\\
   \multicolumn{1}{l@{\vdots}}{}&\\

\texttt{make tidyup}&
      Tidyup before doing a Git commit. Remove all easily generated files, and the large Git repositories needed for the pilot survey. Do not remove the main PDFs, or the \LaTeX\ data include files. Do not remove the .aux files, as \LaTeX\ runs much more smoothly with them.\\
\end{tabular}}

### 2023-02-27 generated/summary-table.tex
Mainly getting mathematica+make to work together

\begin{tabular}{|rrrc|}\hline
Number of papers sampled relying on code&32&100\%&\\\hline\hline
\multicolumn{4}{|l|}{\textbf{Access to code}}\\
Some or all code available&12&38\%&\\
Some or all code in principle available on request&8&25\%&\\
Requested code actually made available (within 2 years 7 months${}^{\star}$)&0&0\%& \\\hline
 \multicolumn{4}{|l|}{{\textbf{Evidence of any software engineering practice}}}\\
Evidence program designed rigorously&{0}&{0\%}&\\
Evidence source code properly tested&{0}&{0\%}&\\
Evidence of any tool-based development&{0}&{0\%}&\\
Team or open source based development&{0}&{0\%}&\\
Other methods, e.g., independent coding methods&{1}&{3\%}&\\\hline
\multicolumn{4}{|l|}{\textbf{Documentation and comments}}\\
Substantial code documentation and comments&2&6\%&\\
Comments explain some code intent&3&9\%&\\
Procedural comments (e.g., author, date, copyright)&10&31\%&\\
No usable comments&17&53\%&\\\hline
\multicolumn{4}{|l|}{\textbf{Repository use}}\\
Used code repository (e.g., GitHub)&9&28\%&\\
Used data repository (e.g., Dryad or GitHub)&9&28\%&\\
Empty repository&1&3\%&\\\hline
\multicolumn{4}{|l|}{{\textbf{Evidence of documented processes}}}\\
Evidence of RAP/\RAPstar\ or any other principles in use to support scrutiny&{0}&{0\%}&\\\hline
\multicolumn{4}{|l|}{\textbf{Adherence to journal code policy (if any)}}\\
Papers published in journals with code policies&26&81\%&\\
Clear breaches of journal code policy (if any) & 11&42\%&(\emph{N}~=~26)\\
\hline\end{tabular}\\
\vskip 1ex ${}^{\star}$Time of 2 years 7 months is wait between code request and date of generating this table.

>>>>

\begin{tabular}{|rrrc|}\hline
Number of papers sampled relying on code&32&100\%&\\\hline\hline
\multicolumn{4}{|l|}{\textbf{Access to code}}\\
Some or all code available&12&38\%&\\
Some or all code in principle available on request&8&25\%&\\
Requested code actually made available (within 2 years 8 months${}^{\star}$)&0&0\%& \\\hline
 \multicolumn{4}{|l|}{{\textbf{Evidence of any software engineering practice}}}\\
Evidence program designed rigorously&{0}&{0\%}&\\
Evidence source code properly tested&{0}&{0\%}&\\
Evidence of any tool-based development&{0}&{0\%}&\\
Team or open source based development&{0}&{0\%}&\\
Other methods, e.g., independent coding methods&{1}&{3\%}&\\\hline
\multicolumn{4}{|l|}{\textbf{Documentation and comments}}\\
Substantial code documentation and comments&2&6\%&\\
Comments explain some code intent&3&9\%&\\
Procedural comments (e.g., author, date, copyright)&10&31\%&\\
No usable comments&17&53\%&\\\hline
\multicolumn{4}{|l|}{\textbf{Repository use}}\\
Used code repository (e.g., GitHub)&9&28\%&\\
Used data repository (e.g., Dryad or GitHub)&9&28\%&\\
Empty repository&1&3\%&\\\hline
\multicolumn{4}{|l|}{{\textbf{Evidence of documented processes}}}\\
Evidence of RAP/\RAPstar\ or any other principles in use to support scrutiny&{0}&{0\%}&\\\hline
\multicolumn{4}{|l|}{\textbf{Adherence to journal code policy (if any)}}\\
Papers published in journals with code policies&26&81\%&\\
Clear breaches of journal code policy (if any) & 11&42\%&(\emph{N}~=~26)\\
\hline\end{tabular}\\
\vskip 1ex ${}^{\star}$Time of 2 years 8 months is wait between code request and date of generating this table.

### 2023-02-27 paper-seb-supplementary-material.tex
Added some conditional Latex to handle temporarily underfined SupplementalLastPage macro
May fix PDF bounding box portability prolem
Generalising image formats - PDF/JPG etc
Mainly getting mathematica+make to work together

\iftrue
    \PassOptionsToPackage{hyphens}{url}
    \documentclass[10pt,a4paper]{article}
    \usepackage[text={6.5in,10in},centering]{geometry}    
    \usepackage{url}
    \usepackage{doi}
    \usepackage{longtable}
    \usepackage{color}
    \usepackage{amsmath,amssymb}
    \usepackage{fancyhdr}
    \usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
    \def\httpURL#1{\href{http://#1}{\textcolor{blue}{#1}}}
    \def\LONGhttpURL#1#2{\href{http://#1}{\textcolor{blue}{#2}}}    
    \input paper-seb-macros.tex
\fi

@@

% pageref gives us a hyperlink which looks unsightly, so we do it this way...
\makeatletter
\def\rememberpage{\immediate\write\@auxout{\bslash gdef\bslash SupplementalLastPage{\thepage}}}
\makeatother

\rfoot{\supplement\ \thepage/\SupplementalLastPage}
\lfoot{\today}
\cfoot{}
\lhead{}
\rhead{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\thispagestyle{empty}

@@

\begin{figure} 
   \centering
   \includegraphics[width=5in]{generated/basic.pdf} 
   \caption{The common basic --- error-prone and obsolete --- approach to scientific authoring is to use code to help generate analyses and diagrams, then manually copy and paste the selected results into the publication. Note that the publication, including the results, can be edited arbitrarily, and typically the results published will have been edited and modified (if only for typographical purposes) from those actually generated by the code.}
   \label{fig:basic}
\end{figure}
\begin{figure} 
   \centering
   \includegraphics[width=5in]{generated/excel.pdf} 
   \caption{When the code is in a spreadsheet, such as Microsoft Excel, the code is generally hidden from sight. The data copied \& pasted into a publication may or may not be calculated from data in other cells (such as column totals). Records are rarely taken of these manual processes, and, anyway, typically it is impossible to be certain exactly what has been copied unless very great care is taken. In consequence, if a spreadsheet is modified, it is haphazard what results are updated and corrected in the publication. }
   \globalLabelValue{excelFigure}{\thefigure}
   \label{fig:excel}
\end{figure}
\begin{figure} 
   \centering
   \includegraphics[width=5in]{generated/import.pdf} 
   \caption{Improving over the normal approach (figure \ref{fig:basic}), data and diagrams are placed in the publication using a programmed, systematic approach. In the present paper, this was done by generating text files of \LaTeX\ definitions (represented by boxes in the central column of the schematic), hence providing \LaTeX\ names for all of the code-generated values. Since the copying of results into a publication is automated and easy, any improvements to the results (such as correcting errors) are made by improving the code --- which therefore contributes to improving all future-generated results too. Not shown, but in well-engineered code, documentation will also be generated, such as by using tools such as JavaDoc or Doxygen.}
   \label{fig:rap}
\end{figure}
\begin{figure}[t]
   \centering
   \includegraphics[width=5in]{generated/notebook.pdf} 
   \caption{In a notebook system, such as \emph{Mathematica\/} or Jupyter, a single document --- the notebook --- integrates the publication, the code, any notes, as well as all the results. The code generates results and images that are automatically (and reliably) inserted in place into the notebook, usually right after the code that generates them. Some parts of the notebook are marked or selected to be printed as the publication, thus allowing most if not all code to be hidden from the final publication. In well-engineered code, the notebook will directly contain full documentation.
Note that in most systems, notebooks can import and generate arbitrary data (images, sounds, sensor data, etc).}
   \label{fig:notebook}
\end{figure}

@@

\begin{table}[t]
\begin{center}
\input generated/make-help.tex
\end{center}
\caption{Conforming to the \RAPstar\ methodology, the abbreviated summary above was generated automatically, by using \texttt{make data}. %(Saying \texttt{make help} would generate a full summary on the command line.)
}
\label{table:options}
\end{table}

>>>>

\iftrue
    \PassOptionsToPackage{hyphens}{url}
    \documentclass[10pt,a4paper]{article}
    \usepackage[text={6.5in,10in},centering]{geometry}    
    \usepackage{url}
    \usepackage{doi}
    \usepackage{longtable}
    \usepackage{color}
    \usepackage{amsmath,amssymb}
    \usepackage{fancyhdr}

    \usepackage{graphicx}
	\PassOptionsToPackage{dvipdfmx}{graphicx}

	\usepackage{amssymb}
	\usepackage{epstopdf}
    \def\httpURL#1{\href{http://#1}{\textcolor{blue}{#1}}}
    \def\LONGhttpURL#1#2{\href{http://#1}{\textcolor{blue}{#2}}}    
    \input paper-seb-macros.tex
\fi

@@

% pageref gives us a hyperlink which looks unsightly, so we do it this way...
\makeatletter

\def\rememberpage{\immediate\write\@auxout{\bslash gdef\bslash SupplementalLastPage{\thepage}}}

% putting \typeout in the right footer will get repeated warnings (which I hope will be noticed!)
% to complement the red text in the footer itself on every page
\@ifundefined{SupplementalLastPage}{\rfoot{\supplement\ \thepage\ \textcolor{red}{\bf(Rerun to get number of pages)}\typeout{* Rerun to get correct number of pages in the running footer}}}{\rfoot{\supplement\ \thepage/\SupplementalLastPage}}

\makeatother

%\rfoot{\supplement\ \thepage/\SupplementalLastPage}
\lfoot{\today}
\cfoot{}
\lhead{}
\rhead{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\thispagestyle{empty}

@@

\begin{figure} 
   \centering
   \includegraphics[width=5in]{generated/basic.\imageFileSuffix} 
   \caption{The common basic --- error-prone and obsolete --- approach to scientific authoring is to use code to help generate analyses and diagrams, then manually copy and paste the selected results into the publication. Note that the publication, including the results, can be edited arbitrarily, and typically the results published will have been edited and modified (if only for typographical purposes) from those actually generated by the code.}
   \label{fig:basic}
\end{figure}
\begin{figure} 
   \centering
   \includegraphics[width=5in]{generated/excel.\imageFileSuffix} 
   \caption{When the code is in a spreadsheet, such as Microsoft Excel, the code is generally hidden from sight. The data copied \& pasted into a publication may or may not be calculated from data in other cells (such as column totals). Records are rarely taken of these manual processes, and, anyway, typically it is impossible to be certain exactly what has been copied unless very great care is taken. In consequence, if a spreadsheet is modified, it is haphazard what results are updated and corrected in the publication. }
   \globalLabelValue{excelFigure}{\thefigure}
   \label{fig:excel}
\end{figure}
\begin{figure} 
   \centering
   \includegraphics[width=5in]{generated/import.\imageFileSuffix} 
   \caption{Improving over the normal approach (figure \ref{fig:basic}), data and diagrams are placed in the publication using a programmed, systematic approach. In the present paper, this was done by generating text files of \LaTeX\ definitions (represented by boxes in the central column of the schematic), hence providing \LaTeX\ names for all of the code-generated values. Since the copying of results into a publication is automated and easy, any improvements to the results (such as correcting errors) are made by improving the code --- which therefore contributes to improving all future-generated results too. Not shown, but in well-engineered code, documentation will also be generated, such as by using tools such as JavaDoc or Doxygen.}
   \label{fig:rap}
\end{figure}
\begin{figure}[t]
   \centering
   \includegraphics[width=5in]{generated/notebook.\imageFileSuffix} 
   \caption{In a notebook system, such as \emph{Mathematica\/} or Jupyter, a single document --- the notebook --- integrates the publication, the code, any notes, as well as all the results. The code generates results and images that are automatically (and reliably) inserted in place into the notebook, usually right after the code that generates them. Some parts of the notebook are marked or selected to be printed as the publication, thus allowing most if not all code to be hidden from the final publication. In well-engineered code, the notebook will directly contain full documentation.
Note that in most systems, notebooks can import and generate arbitrary data (images, sounds, sensor data, etc).}
   \label{fig:notebook}
\end{figure}

@@

\begin{table}[t]
\begin{center}
\input generated/make-help.tex
\end{center}
\caption{Conforming to the \RAPstar\ methodology, the abbreviated summary above was generated automatically, by using \texttt{make data}. A full list of \texttt{make} options is generated by \texttt{make} or \texttt{make help} when run on the Unix command line. %(Saying \texttt{make help} would generate a full summary on the command line.)
}
\label{table:options}
\end{table}
